Discussion Draft

### 2020-04-15 doc/Discussion.rmd
added to bib

As outlined in Hanel et al 2018, sexual dimorphism in chromatin organization translates to interference strength in base pairs. Since more DNA is sequestered into the radial loops per unit of the central axis, in the chromosome organization with longer DNA loops, as seen in males for mice (Lynn, gruhn) and humans (petkov), interference strength measured in base pairs will be stronger compared to female linkage maps. The signal for interference is mediated though the chromosome axis (Zickler Kleckner), interference strength measured in micrometers of is conserved between sexes [@petkov2007].

(hanel makes connections to the typical (telomere-bias) --(stronger interference pushes the crossovers to the ends)

<just outlined a consequence of sexual dimorphism in chromatin organization... but this isn't conserved as a

-- not confirmed - if this is a conserved pattern / 
pattern - (general pattern for linkage maps, but there's a lack of cytological data for both sexes)

-- the role of chromatin organization in recombination variation landscapes -- should be studied/ (needs more support)

>>>>

As outlined in @haenel2018, sexual dimorphism in chromatin organization translates to interference strength in base pairs. Since more DNA is sequestered into the radial loops per unit of the central axis, in the chromosome organization with longer DNA loops, as seen in males for mice [@petkov2007, @lynn2002], and humans [@gruhn2013], interference strength measured in base pairs will be stronger compared to female linkage maps. The signal for interference is mediated though the chromosome axis [@zicklerKleckner2015], interference strength measured in micrometers of is conserved between sexes [@petkov2007]. The wide spread pattern of stronger interference strength in Mb (and cm/Mb) for male specfic linkage maps is indirect evidence that sexual dimorphism in chromatin organization however this has yet to be confirmed in cytological data from both sexes in species beyond mice and humans.
